### 2024-03-18 sections/0intro.tex

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_alg_disk/M}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem*}
%
Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on and classify factorization algebras on all spheres $S^n$. Only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras, so we should note the result above lets us obtain generalizations without falling back on covering space techniques.

>>>>

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_lcfas}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
    \end{equation}
\end{theorem*}
%
The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology. A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}. This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$. Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.

### 2024-03-18 sections/3algebras.tex

\begin{remark}
    As noted at the beginning of \ss 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables. The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory. 
\end{remark}

>>>>

\begin{remark}
    As noted at the beginning of \S 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables. The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory. 
\end{remark}
